\documentclass{article}

% landscape orientation
\usepackage[landscape]{geometry}

% table spans pages
\usepackage{longtable}

% pass / fail colors
\usepackage{color}
\usepackage[dvipsnames]{xcolor}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\testerName}{}
\newcommand{\commitHash}{}

% \pass and \fail{text} definitions
\newcommand{\pass}{\textcolor{OliveGreen}{PASS}}
\newcommand{\fail}[1]{\textcolor{BrickRed}{FAIL}\footnote{#1}}

% no new page for title
\let\endtitlepage\relax

% more space between table entries
\renewcommand{\arraystretch}{2.8}

\begin{document}

\begin{titlepage}
\begin{center}
\textsc{\huge Plug and Play Test Results} \\ [0.25cm]
\Large Performed on \today \\ [0.5cm]

\begin{minipage}[t]{0.4\textwidth}
\large \emph{Tester:} \\ \testerName
\end{minipage}
\begin{minipage}[t]{0.4\textwidth}
\raggedleft\large\emph{Commit:} \\ \commitHash
\end{minipage}

\vspace{0.5cm}\hrule

\end{center}
\end{titlepage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
\begin{footnotesize}
\begin{longtable}{|p{3cm}|p{4cm}|p{10cm}|c|}
    \hline
    Test Prefix & Description & Expected Result & Result \\ \hline \endhead \hline \endfoot
    Configuration1 & Run the DGI using a negative session port. & Exception caught in main during start up: factory-port=-53000: invalid port number: -53000 & \\
    Configuration2 & Run the DGI using a reserved session port. & Exception caught in main during start up: factory-port=0: reserved port number: 0 & \\
    Configuration3 & Run the DGI using a session port greater than 65535. & Exception caught in main during start up: factory-port=68000: invalid port number: 68000 & \\
    Configuration4 & Run the DGI using a non-numeric session port. & Exception caught in main during start up: factory-port=53000wq: invalid port number: 53000wq & \\
    Configuration5 & Run the DGI without the session port specified. & Plug and Play devices disabled. & \\
    BasicOperation1 & Detect a single plug and play device. & SST (0) $\rightarrow$ 0.0 \newline SST (1) $\rightarrow$ 5.0 & \\
    BasicOperation2 & Remove a plug and play device that has gone off-line. & SST (0) $\rightarrow$ 0.0 \newline SST (1) $\rightarrow$ 5.0 \newline SST (0) $\rightarrow$ 0.0 & \\
    BasicOperation3 & Change the value of a plug and play device at run time. & SST (0) $\rightarrow$ 0.0 \newline SST (1) $\rightarrow$ 5.0 \newline SST (1) $\rightarrow$ 10.0 & \\
    BasicOperation4 & Detect two devices of the same type with the correct $\rightarrow$ value. & SST (0) $\rightarrow$ 0.0 \newline SST (2) $\rightarrow$ 12.0 & \\
    BasicOperation5 & Detect two devices of different types with the correct values. & LOAD (0) $\rightarrow$ 0.0 ; SST (0) $\rightarrow$ 0.0 \newline LOAD (1) $\rightarrow$ 42.0 ; SST (1) $\rightarrow$ 5.0 & \\
    BasicOperation6 & Remove the first of two SST devices. & SST (0) $\rightarrow$ 0.0 \newline SST (2) $\rightarrow$ 12.0 \newline SST (1) $\rightarrow$ 7.0 & \\
    BasicOperation7 & Remove the second of two SST devices. & SST (0) $\rightarrow$ 0.0 \newline SST (2) $\rightarrow$ 12.0 \newline SST (1) $\rightarrow$ 5.0 & \\
    BasicOperation8 & Remove a device other than the SST. & LOAD (0) $\rightarrow$ 0.0 ; SST (0) $\rightarrow$ 0.0 \newline LOAD (1) $\rightarrow$ 42.0 ; SST (1) $\rightarrow$ 5.0 \newline LOAD (0) $\rightarrow$ 0.0 ; SST (1) $\rightarrow$ 5.0 & \\
    BasicOperation9 & Change the value of one of several SST devices. & SST (0) $\rightarrow$ 0.0 \newline SST (2) $\rightarrow$ 12.0 \newline SST (2) $\rightarrow$ 17.0 & \\
    BasicOperation10 & Change the value of a non-SST device. & LOAD (0) $\rightarrow$ 0.0 ; SST (0) $\rightarrow$ 0.0 \newline LOAD (1) $\rightarrow$ 42.0 ; SST (1) $\rightarrow$ 5.0 \newline LOAD (1) $\rightarrow$ 24.0 ; SST (1) $\rightarrow$ 5.0 & \\
    BasicOperation11 & Handle a large number of devices at once. & DRER (0) $\rightarrow$ 0.0 ; DESD (0) $\rightarrow$ 0.0 ; LOAD (0) $\rightarrow$ 0.0 ; SST (0) $\rightarrow$ 0.0 \newline DRER (3) $\rightarrow$ 111.0 ; DESD (1) $\rightarrow$ 10.0 ; LOAD (1) $\rightarrow$ 42.0 ; SST (2) $\rightarrow$ 12.0 & \\
    BasicOperation12 & Change the value of a large number of devices. & DRER (0) $\rightarrow$ 0.0 ; DESD (0) $\rightarrow$ 0.0 ; LOAD (0) $\rightarrow$ 0.0 ; SST (0) $\rightarrow$ 0.0 \newline DRER (2) $\rightarrow$ 39.0 ; DESD (1) $\rightarrow$ 10.0 ; LOAD (1) $\rightarrow$ 42.0 ; SST (1) $\rightarrow$ 5.0 \newline DRER (2) $\rightarrow$ 49.0 ; DESD (1) $\rightarrow$ 10.0; LOAD (1) $\rightarrow$ 42.0 ; SST (1) $\rightarrow$ 10.0 & \\
    Failure1 & Fail before sending the DGI device states. & Removing an adapter due to timeout & \\
    Failure2 & Fail after sending the DGI device states. & SST (0) $\rightarrow$ 0.0 \newline SST (1) $\rightarrow$ 5.0 \newline SST (0) $\rightarrow$ 0.0 & \\
    Failure3 & Sleep after sending the device states and quickly continue. & SST (0) $\rightarrow$ 0.0 \newline SST (1) $\rightarrow$ 5.0 & \\
    Failure4 & Sleep after sending the device states and continue after a delay. & SST (0) $\rightarrow$ 0.0 \newline SST (1) $\rightarrow$ 5.0 \newline SST (0) $\rightarrow$ 0.0 \newline SST (1) $\rightarrow$ 5.0 & \\
    Failure5A & DGI loses Wi-Fi before receiving device states. & Removing an adapter due to timeout & \\
    Failure5B & Controller loses Wi-Fi before sending the DGI device states. & Removing an adapter due to timeout & \\
    Failure6A & DGI loses Wi-Fi before receiving device states and then regains it. & SST (0) $\rightarrow$ 0.0 \newline SST (1) $\rightarrow$ 5.0 & \\
    Failure6B & Controller loses Wi-Fi before sending states and then regains it. & SST (0) $\rightarrow$ 0.0 \newline SST (1) $\rightarrow$ 5.0 & \\
    Failure7A & DGI loses Wi-Fi after receiving device states. & SST (0) $\rightarrow$ 0.0 \newline SST (1) $\rightarrow$ 5.0 \newline SST (0) $\rightarrow$ 0.0 & \\
    Failure7B & Controller loses Wi-Fi after sending the DGI device states. & SST (0) $\rightarrow$ 0.0 \newline SST (1) $\rightarrow$ 5.0 \newline SST (0) $\rightarrow$ 0.0 & \\
    Failure8A & DGI loses Wi-Fi after receiving device states and regains it after a delay. & SST (0) $\rightarrow$ 0.0 \newline SST (1) $\rightarrow$ 5.0 \newline SST (0) $\rightarrow$ 0.0 \newline SST (1) $\rightarrow$ 5.0 & \\
    Failure8B & Controller loses Wi-Fi after sending device states and regains it after a delay. & SST (0) $\rightarrow$ 0.0 \newline SST (1) $\rightarrow$ 5.0 \newline SST (0) $\rightarrow$ 0.0 \newline SST (1) $\rightarrow$ 5.0 & \\
    Failure9A & DGI leaves range of Wi-Fi after receiving device states. & SST (0) $\rightarrow$ 0.0 \newline SST (1) $\rightarrow$ 5.0 \newline SST (0) $\rightarrow$ 0.0 & \\
    Failure9B & Controller leaves range of Wi-Fi after sending device states. & SST (0) $\rightarrow$ 0.0 \newline SST (1) $\rightarrow$ 5.0 \newline SST (0) $\rightarrow$ 0.0 & \\
    Failure10A & DGI leaves range of Wi-Fi after receiving device states, then returns within range after a delay. & SST (0) $\rightarrow$ 0.0 \newline SST (1) $\rightarrow$ 5.0 \newline SST (0) $\rightarrow$ 0.0 \newline SST (1) $\rightarrow$ 5.0 & \\
    Failure10B & Controller leaves range of Wi-Fi after sending device states, then returns within range after a delay. & SST (0) $\rightarrow$ 0.0 \newline SST (1) $\rightarrow$ 5.0 \newline SST (0) $\rightarrow$ 0.0 \newline SST (1) $\rightarrow$ 5.0 & \\
    UnexpectedError1 & Send an unrecognized device type to the DGI. & Rejected client: Unknown device type: SST & \\
    UnexpectedError2 & Send an unrecognized signal type to the DGI. & Unknown device signal: TestController:SST1 gateawy & \\
    UnexpectedError3 & Send a corrupt state value to the DGI. & Corrupt state: received non-numeric value & \\
    UnexpectedError4 & Have the same controller specify the same device twice. & Duplicate device ID: VeryUnfortunateController:Sst1 or The device signal (VeryUnfortunateController:Sst1,gateway) is already registered as state information. & \\
    UnexpectedError5 & Have the same controller start two simultaneous sessions. & Rejected client: Duplicate session for TestController & \\
    UnexpectedError6 & The DGI adapter factory receives a packet with a header it does not recognize & Expected 'Hello' message: BadPacket & \\
    UnexpectedError7 & The DGI adapter receives a packet with a header it does not recognize & Unknown header: BadPacket & \\
    UnexpectedError8 & The DGI adapter factory receives a packet containing a lone Hello command with the wrong delimiter & Connection closed due to timeout. & \\
    UnexpectedError9 & The DGI adapter factory receives a packet containing a lone Hello command followed by nonsense data & Connection closed due to timeout. & \\
    UnexpectedError10 & The DGI adapter factory receives a packet containing nonsense data & Connection closed due to timeout. & \\
    UnexpectedError11 & The DGI adapter receives a packet containing a lone command with the wrong delimiter & Connection closed due to timeout. & \\
    UnexpectedError12 & The DGI adapter receives a packet containing a lone command with the wrong delimiter follwed by nonsense data & Connection closed due to timeout. & \\
    UnexpectedError13 & The DGI adapter receives a packet containing a series of commands with the wrong delimiters & Connection closed due to timeout. & \\
    UnexpectedError14 & The DGI adapter receives a packet containing nonsense data & Connection closed due to timeout. & \\
    MultipleControllers1 & Have two controllers use the same device type with different names. & SST (0) $\rightarrow$ 0.0 \newline \ldots \newline SST (2) $\rightarrow$ 12.0 & \\
    MultipleControllers2 & Have two controllers use the same device type with identical names. & SST (0) $\rightarrow$ 0.0 \newline \ldots \newline SST (2) $\rightarrow$ 12.0 & \\
    MultipleControllers3 & Have two controllers use different device types. & LOAD (0) $\rightarrow$ 0.0 ; SST (0) $\rightarrow$ 0.0 \newline \ldots \newline LOAD (1) $\rightarrow$ 42.0 ; SST (1) $\rightarrow$ 5.0 & \\
    MultipleControllers4 & Remove the first of two controllers connected to the DGI. & LOAD (0) $\rightarrow$ 0.0 ; SST (0) $\rightarrow$ 0.0 \newline \ldots \newline LOAD (1) $\rightarrow$ 42.0 ; SST (1) $\rightarrow$ 5.0 \newline LOAD (1) $\rightarrow$ 42.0 ; SST (0) $\rightarrow$ 0.0 & \\
    MultipleControllers5 & Remove the second of two controllers connected to the DGI. & LOAD (0) ; SST (0) $\rightarrow$ 0.0 $\rightarrow$ 0.0 \newline \ldots \newline LOAD (1) $\rightarrow$ 42.0 ; SST (1) $\rightarrow$ 5.0 \newline LOAD (0) $\rightarrow$ 0.0 ; SST (1) $\rightarrow$ 5.0 & \\
    MultipleControllers6 & Change the device value of a controller connected to the DGI. & SST (0) $\rightarrow$ 0.0 \newline \ldots \newline SST (2) $\rightarrow$ 12.0 \newline SST (2) $\rightarrow$ 17.0 & \\
    MultipleControllers7 & Use a large number of controllers to connect at once. & DRER (0) $\rightarrow$ 0.0 ; DESD (0) $\rightarrow$ 0.0 ; LOAD (0) $\rightarrow$ 0.0 ; SST (0) $\rightarrow$ 0.0 \newline \ldots \newline DRER (3) $\rightarrow$ 111.0 ; DESD (1) $\rightarrow$ 10.0 ; LOAD (1) $\rightarrow$ 42.0 ; SST (2) $\rightarrow$ 12.0 \newline \ldots \newline DRER (3) $\rightarrow$ 121.0 ; DESD (1) $\rightarrow$ 10.0 ; LOAD (1) $\rightarrow$ 42.0 ; SST (2) $\rightarrow$ 17.0 & \\
    MultipleDGI1 & Have two DGI converge to a positive normal value. & \begin{minipage}[t]{0.5\linewidth}SST (0) $\rightarrow$ 0.0 \newline \ldots \newline SST (1) $\rightarrow$ 20.0\end{minipage}\begin{minipage}[t]{0.5\linewidth}SST (0) $\rightarrow$ 0.0 \newline \ldots \newline SST (1) $\rightarrow$ 20.0\end{minipage} & \\
    MultipleDGI2 & Have two DGI converge to a negative normal value. & \begin{minipage}[t]{0.5\linewidth}SST (0) $\rightarrow$ 0.0 \newline \ldots \newline SST (1) $\rightarrow$ -5.0\end{minipage}\begin{minipage}[t]{0.5\linewidth}SST (0) $\rightarrow$ 0.0 \newline \ldots \newline SST (1) $\rightarrow$ -5.0\end{minipage} & \\
    MultipleDGI3 & Have the normal value change during convergence. & \begin{minipage}[t]{0.5\linewidth}SST (0) $\rightarrow$ 0.0 \newline \ldots \newline SST (1) $\rightarrow$ -3.0 \newline \ldots \newline SST (1) $\rightarrow$ -6.0\end{minipage}\begin{minipage}[t]{0.5\linewidth}SST (0) $\rightarrow$ 0.0 \newline \ldots \newline SST (1) $\rightarrow$ -3.0 \newline \ldots \newline SST (1) $\rightarrow$ -6.0\end{minipage} & \\
    MultipleDGI4 & Have one DGI lose its devices during convergence. & \begin{minipage}[t]{0.5\linewidth}SST (0) $\rightarrow$ 0.0 \newline \ldots \newline SST (1) $<$ 250.0\end{minipage}\begin{minipage}[t]{0.5\linewidth}SST (0) $\rightarrow$ 0.0 \newline \ldots \newline SST (0) $\rightarrow$ 0.0\end{minipage} & \\
    MultipleDGI5 & Have one DGI lose one device during convergence. & \begin{minipage}[t]{0.5\linewidth}SST (0) $\rightarrow$ 0.0 \newline \ldots \newline SST (1) $\rightarrow$ 0 \newline \ldots \newline SST (1) $>$ 1 \end{minipage}\begin{minipage}[t]{0.5\linewidth}SST (0) $\rightarrow$ 0.0 \newline \ldots \newline SST (2) $\rightarrow$ 9250.1 \newline \ldots \newline SST (1) $<$ 250.0 \end{minipage} & \\
    MultipleDGI6 & Have one DGI with no attached devices. & \begin{minipage}[t]{0.5\linewidth}SST (0) $\rightarrow$ 0.0 \newline \ldots \newline SST (1) $\rightarrow$ 10.0\end{minipage}\begin{minipage}[t]{0.5\linewidth}SST (0) $\rightarrow$ 0.0\end{minipage} & \\
\end{longtable}
\end{footnotesize}
\end{center}

\end{document}
